Sound Automated Synthesis of Digital Controllers

### 2016-10-12 paper/paper.tex
Updated experiments table data.
Extended experimental discussion.

%---------------------------------
\subsection{Results}
\label{experimental-results}
%---------------------------------

>>>>

%---------------------------------
\subsection{Results}
\label{experimental-results}
We outline the runtimes required to synthesise a stable controller for each
benchmark in Table~\ref{tab:results}. For most benchmarks the conjecture explained
in section~\ref{fixedpoint_verification} holds and the inductive back-end is able
to find a stable solution in less than one minute. This is possible if the inductive
solutions need to be refined with few counterexamples and fixed point precision
increases. However, some of our benchmarks did not meet these criteria. In these
cases the interval arithmetic back-end was able to complement the inductive approach
and synthesise a solution instead, albeit with significantly larger runtimes.

\begin{figure}[H]
\centering
\begin{tabular}{l | r l r l}
Benchmark              & Base     &         & Unc     & \\\cline{1-4}
CruiseControl02        & 17\,s    &         & 46\,s   & \\
SatelliteB2            & 7\,s     &         & 6601\,s & \tbmark\\
SatelliteC2            & 369\,s   & \tbmark & 76\,s   & \tbmark\\
SpringMassDamper       &          &         &         & 
\end{tabular}

\vspace{0.5em}
\scriptsize{* = solved with interval back-end}
\vspace{0.5em}

\caption{Experimental results. \label{tab:results}}
\end{figure}
%---------------------------------

We conclude from these results that the inductive back-end provides excellent performance
for synthesising stable controllers in the majority of the benchmarks, and can be
complemented using the interval arithmetic back-end where the inductive conjectures fail
too frequently. Both back-ends enabled controller synthesis for all benchmarks within
reasonable time frames.
